Reply to Reviewer #1

### 2022-02-06 Writing/Re_JournalSubmission/replies_rev_1.rmd
changes in response to reviewer 1

@@

**3. The description of materials and methods section is redundant, please move some unimportant details description to supplementary materials.**
<span style="color:blue">

>>>>

**Materials and Method to just Method: Monte Carlo Simulations?**

We do see a redundancy of expalining how CF can be used to identify site-specific input recommendations. It is explained twice in 2.2 and 3.2.2, while 2.2 is intended for a more general case than 3.2.2 that is specific to our simulations. Therefore, we decided to take out 2.2. We also renamed 2.1 to "Estimating EOIR and Treatment Effects"

The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations. To this core objective, ML simulations are our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal. However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Instead of this, we believe that it is beneficial to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted. Therefore, we kept 2.3 and 2.4 in the current manuscript.

We talk about identifying site-specific economically optimal input rates in three different places. However, each of them serves distinctive purposes and we would like to keep the current structure if that is acceptable to you.

Section 2.1: bluh bluh
Section 3.: true optimal N
Section 3.: estiamted optimal N

@@

**3. The description of materials and methods section is redundant, please move some unimportant details description to supplementary materials.**

<span style="color:blue">  
We first apologogize that misleading section and subsection titles may have caused confusions about your perceived structural redundancy of this article.

We wrote the initial manuscript with avoiding redundancy in mind and we beleived that we did not have any redundancy in our paper. Therefore, we struggled tremendously to see where the redundancies are. We would really appreciate it if you could specify where you see redundancies and why so that we can address prorperly.

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our manuscript is appropriate. Therefore, we had very hard time telling which is unnecessary and not. We would really appreciate it if you could specify which parts are not critical.
